West Africa cuckoo stopover rainfall patterns

### 2018-05-30 stopover_rainfall_vis.Rmd
Now working with rainfall and ndvi

int_out<-read.csv('data/spring_rainfall_by_stopover.csv', h=T)

dat<-read.csv("data/stopover_bestofday_1daymin_recalc_spring_mig_summary_extras.csv", h=T)

@@

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding, "   Mig speed:", round(dtemp$m4c_resid, 2)))

>>>>

int_out<-read.csv('data/spring_rainfall_NDVI_by_stopover_2018_dead.csv', h=T)

dat<-read.csv("data/stopover_bestofday_2018_1daymin_recalc_spring_mig_summary_dead.csv", h=T)

@@

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_bar(data=t2, aes(x=variable, y=value2*500, group=1), stat='identity', fill='red', linetype=0, alpha=1/3)+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))

#"   Mig speed:", round(dtemp$m4c_resid, 2)
